Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-02 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Outline.

Lightning talks is a new feature in WSSSPE2. Every talk in it were given only two
minutes.

\katznote{You could write to everyone and ask for a short summary of their talks
- perhaps 1-3 sentences}

>>>>

Lightning talks is a new feature in WSSSPE2. Every talk in it were given only
two minutes and the space of one slide. A total of 18 lightning talks were
selected in reverse alphabetic order of speakers' last names.
\begin{enumerate}
\item Greg Wilson: Close Enough for Scientific Work

\item Colin Venters: The Nebuchadnezzar Effect: Dreaming of Sustainable Software
through Sustainable Software Architectures

\item James Spencer: Developing New Developers

\item Erin Robinson:  Sustaining Science Bazaars

\item Marlon Pierce: Patching It Up, Pulling It Forward

\item John W Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub

\item Abani Patra: Execute it

\item Christopher Lenhardt: Open Science for Synthesis (OSS): Filling the Gap in
Early Career Training

\item Daniel S. Katz: Implementing Transitive Credit with JSON-LD

\item Samin Ishtiaq: Daemons, Notifications and Sustaining Software

\item James Howison: Retract all Bit-Rotten Publications

\item Sarah Harris: Sustainability of Multidisciplinary Software: A Science
Perspective

\item Marcus D. Hanwell: We Need Tool Builders for Sustainable Scientific
Software

\item Ted Habermann: Communities as the Whole Product

\item Robert R. Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices

\item Carl Boettiger: rOpenSci: building sustainable software by fostering a
diverse community

\item Jakob Blomer: The Need for a Versioned Data Analysis Environment

\item Alice Allen: Find it! Cite it!
\end{enumerate}
